E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-13 System/components.tex
fixed most emph/quote/texttt issues

The E-Mail Field Checker searches for the words `e-mail', `mail' or `email' within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}). This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \dq{\texttt{id}} or \dq{\texttt{name}} set to `email', instead of an actual e-mail field, for purposes of backward compatibility with older browsers.

Compared to searching for explicit e-mail fields, by searching for the presence of the words `e-mail', `mail' or `email' in the form, we are assured very few false negatives. This is because our system is bound to find e-mail fields with their \dq{\texttt{type}}, \dq{\texttt{name}}, or \dq{\texttt{id}} set to one of these words. The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline. However, despite the advantages, this might also lead to a false positive rate. We discuss this possibility in detail in Section \ref*{issues:fpr} - Design Issues.

@@

\subsubsection{E-Mail Form Retriever}
\label{Comp:EMFR}
The E-Mail Form Retriever is the first stage in the Payload Injection Pipeline. It has the following important functions:
\begin{itemize}
	\item Retrieve the newly inserted forms in the `\lstinline{email_forms}' table, checking to ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the data stored in the `\lstinline{form}' table, complete with input fields and their values.
	\item Construct the URL for the `action' attribute of the form so that we can send the HTTP request to the correct URL. 
\end{itemize}

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- `reguser(xxxx)@example.com', where `xxxx' is replaced by our internal `\lstinline{form_id}', to create a one-to-one mapping of the payloads to the forms, and `example.com' is replaced by the required domain. In our case, this domain was `wackopicko.com'.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
In the malicious payload scenario, we inject the fields with the \dq{\texttt{bcc}} (blind carbon copy) element. If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the `bcc' field.

We consider a special case: the addition of a \dq{\texttt{x-check:in}} header field to the payloads. This is due to Python's exhibited behavior when attaching
headers. Instead of overwriting a header if it is already present, it ignores duplicate headers. So, in case the \dq{\texttt{bcc}} field is already present as part of the headers, our injected \dq{\texttt{bcc}} header would be ignored. To overcome this, we need to inject a new header that is not likely to be generated by the web application. Hence, we inject our own \dq{\texttt{x-check:in}} header to ensure we can get results if the injection was successful.

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
\lstset{language=html}
\begin{enumerate}
	\item
	%inside the lstinline, we need to use \\ for \textbackslash
	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the `bcc' field.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: `\textbackslash{}r\textbackslash{}n' is the `Carriage Return - New Line (CRLF)' used on Windows systems. 
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \dq{\texttt{x-check:in}} header is to inject Python based websites.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional `\textbackslash{}r' for Windows compatibility.

\end{enumerate}
The `xxxx' in all of the payloads is replaced by our internal `\lstinline{form_id}', so as to create a one-to-one mapping of the payloads to the forms. The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

@@

\subsubsection{E-Mail Analyzer}
\label{Comp:EMA}
The E-Mail Analyzer checks for the presence of injected data in the received e-mails. This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
\paragraph{Analyzing regular e-mail}
`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where `xxxx' is our internal `\lstinline{form_id}' --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.

To find this, we read through each received e-mail, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the e-mail. If they do, we add them to the list of fields that can potentially result in an E-Mail Header Injection for the given e-mail. we then pass on this information back to the Fuzzer pipeline, along with the `\lstinline{form_id}', so that the Fuzzer can now inject the malicious payloads into the same form.

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@wackopicko.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by `maluser' account directly indicate the presence of the injected `bcc' field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected x-check headers}
E-Mails not received by the `maluser' account but by the `nuser' account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \dq{\texttt{bcc}} part of the payload, thereby sending e-mails only to the `nuser' account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \dq{\texttt{bcc}} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \dq{\texttt{x-check}}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}
\subsubsection{Database}
We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:
\begin{enumerate}
	\item The data is used to validate our findings.
	\item The data collected can be used for other research projects in this area.
\end{enumerate}
Each table in our database is listed in Table~\ref{tab:dbtf} along with the data it is designed to hold. A schema of the database is shown in Figure~\ref{fig:dbschema}.

>>>>

The E-Mail Field Checker searches for the words \texttt{e-mail}, \texttt{mail} or \texttt{email} within the form, instead of an explicit e-mail field (e.g.,\ \colorbox{lightgray}{\lstinline{<input type="email">}}). This is by design, taking into account a very common design pattern used by web developers, where they may have a text field with an \texttt{id} or \texttt{name} set to \texttt{email}, instead of an actual e-mail field, for purposes of backward compatibility with older browsers.

Compared to searching for explicit e-mail fields, by searching for the presence of the words \texttt{e-mail}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives. This is because our system is bound to find e-mail fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words. The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline. However, despite the advantages, this might also lead to a false positive rate. We discuss this possibility in detail in Section \ref*{issues:fpr} - Design Issues.

@@

\subsubsection{E-Mail Form Retriever}
\label{Comp:EMFR}
The E-Mail Form Retriever is the first stage in the Payload Injection Pipeline. It has the following important functions:
\begin{itemize}
	\item Retrieve the newly inserted forms in the \texttt{email\_forms} table, checking to ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the data stored in the \texttt{form} table, complete with input fields and their values.
	\item Construct the URL for the \texttt{action} attribute of the form so that we can send the HTTP request to the correct URL. 
\end{itemize}

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain. In our case, this domain was \texttt{wackopicko.com}.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
In the malicious payload scenario, we inject the fields with the \texttt{bcc} (blind carbon copy) element. If the vulnerability is present, this will cause the server to send a copy of the e-mail to the e-mail address we added as part of the \texttt{bcc} field.

We consider a special case: the addition of a \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
headers. Instead of overwriting a header if it is already present, it ignores duplicate headers. So, in case the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored. To overcome this, we need to inject a new header that is not likely to be generated by the web application. Hence, we inject our own \texttt{x-check:in} header to ensure we can get results if the injection was successful.

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
\lstset{language=html}
\begin{enumerate}
	\item
	%inside the lstinline, we need to use \\ for \textbackslash
	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems. 
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.

\end{enumerate}
The \texttt{xxxx} in all of the payloads is replaced by our internal \texttt{form\_id}, so as to create a one-to-one mapping of the payloads to the forms. The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

@@

\subsubsection{E-Mail Analyzer}
\label{Comp:EMA}
The E-Mail Analyzer checks for the presence of injected data in the received e-mails. This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
\paragraph{Analyzing regular e-mail}
`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.

To find this, we read through each received e-mail, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the e-mail. If they do, we add them to the list of fields that can potentially result in an E-Mail Header Injection for the given e-mail. we then pass on this information back to the Fuzzer pipeline, along with the \texttt{form\_id}, so that the Fuzzer can now inject the malicious payloads into the same form.

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@wackopicko.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected x-check headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}
\subsubsection{Database}
We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:
\begin{enumerate}
	\item The data is used to validate our findings.
	\item The data collected can be used for other research projects in this area.
\end{enumerate}
Each table in our database is listed in Table~\ref{tab:dbtf} along with the data it is designed to hold. A schema of the database is shown in Figure~\ref{fig:dbschema}.

### 2016-05-13 System/issues.tex
chap3 added
fixed most emph/quote/texttt issues

\section[Issues]{Design Issues}
\label{sys:issues}
This section will describe the issues we faced with the design decisions we made, and how we did our best to mitigate them, and their effect on the system.

\begin{itemize}
	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
	As discussed in Section \ref{Comp:EMFC}, we only search for the words `email', `mail' or `e-mail' (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing. \ref{code:false_positive}.

@@

	The word `E-Mail' on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not. However, as we will see, this is not really a significant issue, as despite being added to the \lstinline{`email_forms'} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form. We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.

@@

	\item URL Construction\\
	The multiple ways in which a URL is specified (i.e.\ Relative and Absolute URLs) complicates the construction of the URL from the `action' attribute of the form.  As an example, the following URLs are all equivalent (as parsed by a browser, assuming we are in the path `www.website.com'):

	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=./mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=http://website.com/mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=www.website.com/mail.php}}
	\end{itemize}
	Add to this, if the form is a self-referencing form\,\footnotemark, and is present in mail.php, the following are equivalent to the above URLs as well:
	\footnotetext{A self-referencing form is one which submits the form data to itself. It includes logic to both display the form and process it. It is a \emph{very} common feature in PHP-based scripts.}
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=""}}
		\item \colorbox{lightgray}{\lstinline{action=#}}
		\item `action' is completely omitted
	\end{itemize}
	Also, relative URLs pose another problem. If the URL of the form page ends with `/' and the `action' specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes. This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

@@

	\item Black-box Testing\\
	The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \dq{\texttt{cc}} or \dq{\texttt{bcc}} headers). We have to manually e-mail the developers to get this feedback.

	\item Mapping responses to requests\\
	As we are generating multiple payloads for each form, and the received e-mail may not contain the name of the domain from which we received the e-mail, it is difficult to map the response e-mails to the right requests. We instead use the `\lstinline{form_id}' as part of the payload to map responses to requests accurately.

>>>>

\subsection[Issues]{Design Issues}
\label{sys:issues}
This section will describe the issues we faced with the design decisions we made, and how we did our best to mitigate them, and their effect on the system.

\begin{itemize}
	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing. \ref{code:false_positive}.

@@

	The word \texttt{E-Mail} on Line 2 will result in our system classifying this form as a potential e-mail form, while it clearly is not. However, as we will see, this is not really a significant issue, as despite being added to the \texttt{email\_forms} table, this form will never be injected in the `fuzzer' due to the absence of the appropriate input field in the form. We chose to go with this design, as it allows us to detect almost every form that provides the capability to send or receive e-mail.

@@

	\item URL Construction\\
	The multiple ways in which a URL is specified (i.e.\ Relative and Absolute URLs) complicates the construction of the URL from the \texttt{action} attribute of the form.  As an example, the following URLs are all equivalent (as parsed by a browser, assuming we are in the path \texttt{www.website.com}):

	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=./mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=http://website.com/mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=www.website.com/mail.php}}
	\end{itemize}
	Add to this, if the form is a self-referencing form\,\footnotemark, and is present in mail.php, the following are equivalent to the above URLs as well:
	\footnotetext{A self-referencing form is one which submits the form data to itself. It includes logic to both display the form and process it. It is a \emph{very} common feature in PHP-based scripts.}
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=""}}
		\item \colorbox{lightgray}{\lstinline{action=#}}
		\item \texttt{action} is completely omitted
	\end{itemize}
	Also, relative URLs pose another problem. If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes. This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

@@

	\item Black-box Testing\\
	The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We have to manually e-mail the developers to get this feedback.

	\item Mapping responses to requests\\
	As we are generating multiple payloads for each form, and the received e-mail may not contain the name of the domain from which we received the e-mail, it is difficult to map the response e-mails to the right requests. We instead use the \texttt{form\_id} as part of the payload to map responses to requests accurately.

### 2016-05-13 System/proof_of_concept.tex
fixed most emph/quote/texttt issues

We tested for the headers being injected in real-time by running an instance of MailCatcher, set to listen on all SMTP messages. A sample screenshot of a fuzzed request for the Ruby backend (generated in PostMan) is shown in Figure~\ref{fig:postmanruby}. The e-mail sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}. It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \dq{\texttt{Subject}} field with our message, `hello'.

A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}. The astute reader might have noticed that in the given examples we have used `\%0a' to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used `\textbackslash{}n'. This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

>>>>

We tested for the headers being injected in real-time by running an instance of MailCatcher, set to listen on all SMTP messages. A sample screenshot of a fuzzed request for the Ruby backend (generated in PostMan) is shown in Figure~\ref{fig:postmanruby}. The e-mail sent due to injecting this payload (as captured by MailCatcher) is shown in Figure~\ref{fig:mailcatcherruby}. It can be seen that the headers have been added to the resulting e-mail, and we have successfully managed to overwrite the \texttt{Subject} field with our message, `hello'.

A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}. The astute reader might have noticed that in the given examples we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}. This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

### 2016-05-13 conclusion.tex
fixed most emph/quote/texttt issues

We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the `mail' function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.

>>>>

We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the \texttt{mail} function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.

### 2016-05-13 data_analysis.tex
fixed most emph/quote/texttt issues

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with `bcc' header & 180\\
		\hline
		2 & E-Mail Header Injections with `x-check' header & 153\\
		\hline
		3 & `To header' injections alone & 83\\
		\hline
		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 136\\
		\hline
		5 & Both `To header' injections and x-check headers & 9\\
		\hline
		6 & `x-check' headers found in `nuser' e-mails & 40\\
		\hline
		7 & Unique `x-check' headers found in `nuser' e-mails & 16\\
		\hline
	\end{tabular}
	\caption[\titlecap{Analysis of the data}]{Classification of the e-mails that we received into broad categories of the vulnerability.}
	\label{tab:analysis}
\end{table}

>>>>

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with \texttt{bcc} header & 180\\
		\hline
		2 & E-Mail Header Injections with \texttt{x-check} header & 153\\
		\hline
		3 & \texttt{To header} injections alone & 83\\
		\hline
		4 & E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 136\\
		\hline
		5 & Both \texttt{To header} injections and x-check headers & 9\\
		\hline
		6 & \texttt{x-check} headers found in \texttt{nuser} e-mails & 40\\
		\hline
		7 & Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 16\\
		\hline
	\end{tabular}
	\caption[\titlecap{Analysis of the data}]{Classification of the e-mails that we received into broad categories of the vulnerability.}
	\label{tab:analysis}
\end{table}

### 2016-05-13 introduction.tex
fixed most emph/quote/texttt issues

	Our research focuses on a lesser known injection attack known as E-Mail Header Injection. E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}. The vulnerability exists in the reference implementation of the built-in \dq{\texttt{mail}} functionality in popular languages like PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

>>>>

	Our research focuses on a lesser known injection attack known as E-Mail Header Injection. E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}. The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

### 2016-05-13 rel_work.tex
chap7 added
fixed most emph/quote/texttt issues

\chapter{Related Work}

@@

The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. `To' e-mail header has a corresponding `To' SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like `Ruby Mail' and `JavaMail'. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, `Contact Form', with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to \cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject websites with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences. Also, since we are only injecting a payload with the `bcc' header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.

%The next and final chapter starts by outlining our contributions and closes with concluding remarks about the project.

>>>>

\section{Related Work}

@@

The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to \cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject websites with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences. Also, since we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.
